TGI Spinal Analysis Code

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
adding density plots for VAS ratings

# then remove NaNs
df_long <- df_long %>% filter(!is.na(VAS))
# remove the initial trials - not important for now
init_burn <- filter(df_long, quality == 'init')
all_vas <- filter(df_long, quality != 'init')

# calculate means
vas_meds <- aggregate(VAS ~ quality*manipulation*cold_probe*ID, median, data = all_vas)
# then plot :D
blue <- brewer.pal(6, "Blues")
grey <- brewer.pal(6, "Greys")

ggplot(vas_meds, aes(cold_probe, VAS, colour = manipulation, group = ID)) +
  geom_point(position = position_dodge(.2)) +
  facet_wrap(~quality) +
  scale_colour_manual(values = c(grey[3], blue[4])) +
  theme_bw()
```

>>>>

# then remove NaNs
df_long <- df_long %>% filter(!is.na(VAS))
# remove the initial trials - not important for now
init_burn <- filter(df_long, quality == 'init')
all_vas <- filter(df_long, quality != 'init')
# order the labelling of quality so it is cold, warm, burn

# plot distribution of data
ggplot(all_vas) +
  geom_density(aes(VAS, colour = manipulation)) +
  facet_wrap(~quality, scales = "free") +
  theme_bw()
```
# MAIN HYPOTHESES
# Plot descriptives for each hypotheses
Hypothesis 1: within vs. across dermatomes

```{r}
# calculate means
vas_meds <- aggregate(VAS ~ quality*manipulation*cold_probe*ID, median, data = all_vas)
vas_h1 <- aggregate(VAS)
# then plot :D
blue <- brewer.pal(6, "Blues")
grey <- brewer.pal(6, "Greys")

ggplot(vas_meds, aes(cold_probe, VAS, colour = manipulation, group = ID)) +
  geom_point(position = position_dodge(.2)) +
  facet_grid(~quality*manipulation) +
  scale_colour_manual(values = c(grey[3], blue[4])) +
  theme_bw()
```

Hypothesis 2 a & b: relative location of warm and cold
